Output Summary

### 2023-07-15 03-post-process/ms-content/ms-content.Rmd
Add ms-content figure: comparison of transition rates
LH type apportionment and maturation rates

surv_compare_caption = "
  Survival probability parameters estimated by the state-space model, separated by stage transition and other demographic features (migratory type, origin, population) where applicable.
  Small points show posterior means of year-specific realized values (jitter for visual effect only) and large points show the average across years.
  Information about mortality due to sources/stages not displayed here was either assumed known without error (e.g., prespawn mortality) or expressed as strong prior information with no inter-annual variability (i.e., mortality experienced in ocean-1 $\\to$ ocean-2 and ocean-2 $\\to$ ocean-3).
"
```

@@

>>>>

surv_compare_caption = "
  Survival probability parameters estimated by the state-space model, separated by stage transition and other demographic features (migratory type, origin, population) where applicable.
  Small points show posterior means of year-specific realized values (jitter for visual effect only) and large points show the average across years.
  Information about mortality due to sources/stages not displayed here was either assumed known without error (e.g., prespawn mortality) or expressed as strong prior information with no inter-annual variability (i.e., mortality experienced in ocean-1 $\\to$ ocean-2 and ocean-2 $\\to$ ocean-3).
"

apportion_compare_caption = "
  Transition probability parameters (unrelated to survival) estimated by the state-space model, separated by life stage and origin where applicable.
  Small points show posterior means of year-specific realized values (jitter for visual effect only) and large points show the average across years.
"

@@

```{r apportion-compare-fig, fig.width = 3.4, fig.height = 8 * (3/4.5), fig.cap = msdown::prep_caption(apportion_compare_caption), time_it = TRUE, eval = params$apportion_compare_fig}

# extract the posterior means to plot
pi_fall = array_format(post_summ(post, sub_index("^pi[year,LH_type,pop]", year = observable, pop = ".+", LH_type = i_fall))["mean",])[,i_fall,]
psi_O1_nor = array_format(post_summ(post, sub_index("^psi_O1[year,origin,pop]", year = observable, pop = ".+", origin = o_nor))["mean",])[,o_nor,]
psi_O1_hor = array_format(post_summ(post, sub_index("^psi_O1[year,origin,pop]", year = observable, pop = ".+", origin = o_hor))["mean",])[,o_hor,]
psi_O2_nor = array_format(post_summ(post, sub_index("^psi_O2[year,origin,pop]", year = observable, pop = ".+", origin = o_nor))["mean",])[,o_nor,]
psi_O2_hor = array_format(post_summ(post, sub_index("^psi_O2[year,origin,pop]", year = observable, pop = ".+", origin = o_hor))["mean",])[,o_hor,]

# set MIN to NA for HOR values
psi_O1_hor[,j_min] = NA
psi_O1_hor[,j_min] = NA

mypar(mfrow = c(1,1), oma = c(1.5,1,0,1), col.axis = "black")
layout(matrix(1:3, ncol = 1), height = c(1,1,1))
f_horiz(ests1 = pi_fall, ests2 = NULL, lim = c(0, 0.6), label = "(a) Pr(Fall Migrant)")

f_horiz(ests1 = psi_O1_nor, ests2 = psi_O1_hor, lim = c(0,0.4), label = "(b) Pr(Mature Age-3)")
legend_f("Origin", "NOR", "HOR")

f_horiz(ests1 = psi_O2_nor, ests2 = psi_O2_hor, lim = c(0,1), label = "(c) Pr(Mature Age-4)")
legend_f("Origin", "NOR", "HOR", "bottomleft")

axis_labels("Transition Probability (Non-Survival)")
```
